\documentclass{resume} % use the resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
	pdfborderstyle={/S/U/W 1},
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=green!70!black
}

\name{Shaw Vrana}
\address{(415) 828-0238 \\ San Francisco, CA \\ \href{https://vranix.com}{https://vranix.com} \\ shaw@vranix.com}

\begin{document}

\begin{rSection}{Summary}
Software engineering generalist with experience ranging from Linux kernel to user interface development. Interests include
early stage startups, distributed systems and managing infrastructure at scale.
\end{rSection}

\begin{rSection}{Experience}

\begin{rSubsection}{\href{https://conductorone.com}{ConductorOne}}{2020 - 2022}{Software Engineer}{}
\item Full-stack web development during C1's seed stage. Slack integration.
\end{rSubsection}

\begin{rSubsection}{\href{https://synthesis.ai}{Synthesis AI}}{2019 - 2020}{Head of Software Engineering}{}
\item Built and designed a scalable platform for synthetic image generation.
\end{rSubsection}

\begin{rSubsection}{\href{https://wish.com}{Wish}}{2015 - 2019}{Member of Technical Staff}{}
\item Product search, data pipeline construction, backend performance improvements and infrastructure automation.
\end{rSubsection}

\begin{rSubsection}{\href{https://lookout.com}{Lookout}}{2012 - 2015}{Senior Software Engineer}{}
\item Android development for the Lookout Mobile Security app and Ruby backend web development for the Lookout for Business team.
\end{rSubsection}

\begin{rSubsection}{\href{https://riverbed.com}{Riverbed Technology}}{2005 - 2011}{Member of Technical Staff}{}
\item Linux kernel network engineer for the SteelHead wan optimization product, concentrating on network visibility.
Maintenance and development of this transparent TCP proxy. Created and managed NetFlow integration and IPv6.
\end{rSubsection}

\end{rSection}


\begin{rSection}{Education}
{\bf Vanderbilt University} \hfill {\em 1995 - 1999}
\\ Bachelor of Science, Philosophy and Computer Science
\end{rSection}


\begin{rSection}{Skills}
Experience with Go and Haskell, Kubernetes and Pulumi
\end{rSection}

\begin{rSection}{Projects}
	{\bf Viz} \hfill {\em 2012 - 2014}
\\ A video downloader and player for Android that was downloaded over 10 million times before being removed by Google.
\end{rSection}

\end{document}
